Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-05-28 thesis/abstract.tex
Edits from KVJ, JT, and MM for abstract and intro

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to better understand two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
%In this \thesis
we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star. We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows. This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.

@@

Focusing on the evolution of individual metals within this galaxy, it remains an outstanding question as to what degree (if any) metal mixing processes in a multi-phase ISM influence observed stellar abundance patterns. To address this issue, we characterize the time evolution of the metal mass fraction distributions of each of the tracked elements in our simulation in each phase of the ISM. For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, neutral gas up to hot, ionized gas) that depends upon the energetics of the enrichment sources that dominate the production of a given metal species. We find that AGB wind elements have much broader distributions (i.e. are poorly mixed) as compared to elements released in supernovae. In addition, we demonstrate that elements dominated by AGB wind production are retained at a much higher fraction than elements released in core collapse supernovae (by a factor of $\sim$ 5).

@@

Finally, we summarize how this new understanding of galactic chemical evolution -- that metal mixing and ejection from galaxies is not uniform across metal species -- can be used to improve significantly upon current state of the art galactic chemical evolution models. These improvements stand to help improve our understanding of galactic chemical evolution and reconcile outstanding disagreements between current models and observations.

>>>>

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
%In this \thesis
we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star. We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to trace how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows. This study is directed with the ultimate goal of leveraging the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies to understand galactic evolution.

@@

Focusing on the evolution of individual metals within this galaxy, it remains an outstanding question as to what degree (if any) metal mixing processes in a multi-phase ISM influence observed stellar abundance patterns. To address this issue, we characterize the time evolution of the metal mass fraction distributions of each of the tracked elements in our simulation in each phase of the ISM. For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, neutral gas up to hot, ionized gas) that depend upon the energetics of the enrichment sources that dominate the production of a given metal species. We find that AGB wind elements have much broader distributions (i.e. are poorly mixed) as compared to elements released in supernovae. In addition, we demonstrate that elements dominated by AGB wind production are retained at a much higher fraction than elements released in core collapse supernovae (by a factor of $\sim$ 5).

@@

Finally, we summarize how this improved physical model of galactic chemical evolution that demonstrates that metal mixing and ejection from galaxies is not uniform across metal species can be used to improve significantly upon current state of the art galactic chemical evolution models. These improvements stand to help improve our understanding of galactic chemical evolution and reconcile outstanding disagreements between current models and observations.

### 2019-05-28 thesis/acknowledgments.tex
Edits from KVJ, JT, and MM for abstract and intro

To my wife Ellen, who moved across the country for me to NYC
(and across the country again in the next few months), who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \Dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but its a good thing
I have the rest of my life to show how grateful I am.

>>>>

To my wife Ellen, who moved across the country for me to NYC
(and across the country again in the next few months), who has patiently put up with
all of my travel and time away at conferences in the past few years,
who has worked longer hours at much more demanding jobs than the work I have put
into this \Dissertation, and who has continued to support me through this
entire journey, all just so that I could pursue my dream. A simple ``thank you" is
entirely insufficient to repay her for these sacrifices, but it is a good thing
I have the rest of my life to show how grateful I am.
